\section{Dataset}
\label{sec:dataset}

\subsection{Platform: Men\'eame}

Men\'eame\footnote{\url{https://meneame.net}} is Spain's largest social news aggregation platform, operational since 2005.
Users submit links to news articles from external sources, and the community votes and comments on submissions.
Each story accumulates a score (net upvotes) and a comment section where individual comments receive karma scores (upvotes minus downvotes).
This karma mechanism provides a fine-grained signal of community agreement or disagreement with individual contributions.

\subsection{Data Collection}

We collected 186,318 news stories and their associated 13,252,609 comments spanning 2005--2021 from a publicly available Men\'eame archive.
User identifiers were pseudonymized using SHA-256 hashing to comply with ethical data handling practices.

\subsection{Processing Pipeline}

The raw data was processed through a five-step pipeline:

\paragraph{Step 1: Ingestion.}
JSON files were parsed and consolidated into two Parquet datasets: articles (186,317 rows, 15 columns) and comments (13.2M rows, 7 columns including text, author, karma, and timestamp).

\paragraph{Step 2: Filtering and Subsampling.}
Articles were filtered to remove duplicates, articles with fewer than 5 comments, and outlets with fewer than 3 articles, yielding 168,688 articles.
A stratified subsample of 14,995 articles was selected to ensure representation across outlets, years, and score distributions.

\paragraph{Step 3: Automatic Bias Labeling.}
Articles were labeled using a DistilBERT classifier fine-tuned on the MBBMD dataset \cite{rodrigo2025mbbmd}, a manually annotated corpus of Spanish news articles with 12 annotators per document.
The model assigns each article a bias probability $p \in [0,1]$ and a binary label (biased if $p > 0.5$).
Of the 14,995 articles, 9,225 (61.5\%) were labeled as biased and 5,770 (38.5\%) as non-biased, with a mean bias probability of 0.616.

\paragraph{Step 4: Interaction Feature Extraction.}
For each article, we computed 17 interaction features from the associated comments (Table~\ref{tab:features}).
Features capture karma distributions (mean, median, standard deviation, IQR, entropy, Gini coefficient), engagement metrics (comment count, unique commenters, comments per commenter), temporal dynamics (activity duration, time to first 10 comments), and comment properties (average length).

\paragraph{Step 5: Sentiment Analysis.}
A stratified sample of 20,000 comments (10,000 from biased articles, 10,000 from non-biased) was analyzed using the \texttt{robertuito} sentiment and emotion models \cite{perez2022robertuito}, yielding per-comment labels for sentiment (positive, neutral, negative) and emotions (joy, anger, sadness, fear).

\begin{table}[t]
\centering
\small
\begin{tabular}{ll}
\toprule
\textbf{Category} & \textbf{Features} \\
\midrule
Karma & mean, median, std, IQR, range, \\
 & entropy, Gini, \% negative, \% positive \\
Engagement & score, \# comments, unique commenters, \\
 & comments per commenter \\
Temporal & activity duration (hours), \\
 & time to 10th comment \\
Content & avg comment length, text length, \\
 & \# tags, hour of day, is\_weekend \\
\bottomrule
\end{tabular}
\caption{Interaction features extracted per article.}
\label{tab:features}
\end{table}

\subsection{Dataset Statistics}

Table~\ref{tab:dataset_stats} summarizes the dataset.
The data spans 17 years, 2,868 media outlets, and 96,034 unique commenters.
The most represented outlets are \textit{eldiario.es} (495 articles), \textit{elmundo.es} (430), and \textit{20minutos.es} (413).

\begin{table}[t]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Statistic} & \textbf{Value} \\
\midrule
Articles (subsample) & 14,995 \\
Comments (full) & 13,252,609 \\
Unique commenters & 96,034 \\
Media outlets & 2,868 \\
Time span & 2005--2021 \\
Biased articles & 9,225 (61.5\%) \\
Non-biased articles & 5,770 (38.5\%) \\
Mean bias probability & 0.616 \\
Avg.\ comments/article & 71.3 \\
\bottomrule
\end{tabular}
\caption{Dataset statistics.}
\label{tab:dataset_stats}
\end{table}

\subsection{Data Availability}

The processed dataset, including articles with features, karma distributions, sentiment annotations, and user-outlet interaction data, is publicly available on Zenodo under a CC-BY 4.0 license.\footnote{\url{https://doi.org/10.5281/zenodo.19164549}}
The full processing pipeline is available on GitHub.\footnote{\url{https://github.com/franfj/media-bias-mining-crowd}}
